---
title: "Weißlichtspektren"
output:
  html_document:
    df_print: paged
---
<!--- Change width options to apppropiate values for your desired page size-->
<!--- Important for printing HTML as PDF-->
<style type="text/css">
.main-container {
  width: 20cm;
  max-width: 20cm;
  min-width: 20cm;
  margin-left: auto;
  margin-right: auto;
}
</style>

+ Weißlichspektren herunterladen

```{r, library-and-downloads, waring=F, message=F, results='hide'}
#
# CHARACTERISING THE WITEC DETECTOR
#
# How does the detector response changes when changing the orientation of the lasers plane of polarisation?

#
# Get some libraries and functions used for characterising the detector and plotting stuff
#
source("../bauteilCharakterisierung/charakterisierungDetektor_utilities.R")



# Fetch experimental data from elabFTW
# First try
detector.spectra1 <- GET.elabftw.bycaption(76, header=T, outputHTTP=T) %>% parseTimeSeries.elab(., header=F, sep="")
# Second try
detector.spectra2 <- GET.elabftw.bycaption(81, header=T, outputHTTP=T) %>% parseTimeSeries.elab(., header=F, sep="")
```
+ Berechnen des gemittelten Spektrums
+ Berechnen von absoluter und relativer Differenz zwischen Spektren und ihrem Mittel

```{r, processing}
# Select one data set for evaluation
detector.spectra <- detector.spectra2

#
# PREPROCESS SPECTRA
# Vector normalisation and wavenumber conversion and mean calculation
#
# Wavelength of the WiTecs laser
laser.wavelength <- 514.624
detector.spectra <- lapply(detector.spectra, function(spec) {
  # Which columns contain the measured white lamp spectra?
  data.selector <- which(colnames(spec) %in% c("wavenumber", "wavelength", "mean") == F)
  
  # Convert raman shift in wavenumbers into absolute wavelength
  spec$wavelength <- 1/( 1/laser.wavelength - spec$wavenumber*1e-7 )
  
  # Vector normalisation of the spectra
  # spec[, data.selector] <- apply(spec[, data.selector], 2, function(spec) { spec / sum(spec^2) }) 
  
  # Compute mean spectrum and add it to the data.frame
  spec$mean <- rowMeans(spec[, data.selector])
  
  # Reorder data.frame
  spec <- spec[,c( which(colnames(spec) == "wavenumber"), 
                   which(colnames(spec) == "wavelength"), 
                   which(colnames(spec) == "mean"), 
                   data.selector )]
  # Return
  return(spec)
})

#
# HOW DOES THE INFLUENCE OF THE POLARISATION CHANGE WITH THE WAVENUMBER?
#
detector.absDifference <- lapply(detector.spectra, function(spectra) {
  # Copy white lamp spectrum
  diffSpectra <- spectra
  # Compute the absolute difference between white lamp spectra and their mean spectrum
  diffSpectra[, -(1:3)] <- apply(diffSpectra[, -(1:3)], 2, function(spec) {spec - diffSpectra$mean})
  # Return result
  return(diffSpectra)
})
detector.relDifference <- lapply(detector.spectra, function(spectra) {
  # Copy white lamp spectrum
  diffSpectra <- spectra
  # Compute the relative difference between white lamp spectra and their mean spectrum
  diffSpectra[, -(1:3)] <- apply(diffSpectra[, -(1:3)], 2, function(spec) {(spec/diffSpectra$mean)-1})
  # Return result
  return(diffSpectra)
})
```

+ Alle gemessenen Spektren übereinander legen
+ Das Spektrum der Kalibrationslampe plotten 

```{r, plotting-all-2d}
#
# PLOT
#

# Get the ideal white lamp spectrum
detector.whitelamp <- read.table(file = "../Weisslichtspektrum_Julian.txt", header = T)
# Plot ideal white lamp spectrum
detector.range <- detector.spectra[[1]]$wavelength[c(1, nrow(detector.spectra[[1]]))]
plot(detector.whitelamp, type = "l", 
     main = "Spektrum Kalibrationslampe",
     xlab = expression(bold("wavelength / nm")),
     ylab = expression(bold("intensity")))
abline(v = detector.range)
text( mean(detector.range),
      y = mean(detector.whitelamp$Intensity), expression("Messbereich \n      WiTec") )

# Plot the white lamp spectra for the detector without the microscope
plot.detector.whitelamp(data=makeSpectraPlotable(detector.spectra[[1]][, -c(2:3)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation+45, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Detector Response for polarised white light (with microscope)",
                        ylab="counts")


# Plot the white lamp spectra for the detector with the microscope
plot.detector.whitelamp(data=makeSpectraPlotable(detector.spectra[[2]][, -c(2:3)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Detector Response for polarised white light (without microscope",
                        ylab="counts")
```

+ Alle gemessenen Spektren als 3D-Plot

```{r, plotting-all-3d}
# Plot the WHITE LAMP SPECTRA in one 3d plot as 3D SURFACE
plot.detector.allSpectra(detector.spectra[[1]][,-c(2:3,21:24)], theta=240)
plot.detector.allSpectra(detector.spectra[[2]][,-c(2:3,21:24)], theta=240)
```

+ Auftragen der Differenzspektren
+ Von den Spektren, die mit dem Mikroskop gemessen wurden, werden die Spektren mit dem größten Unterschied gezeigt

```{r, plotting-diff}
# Plot the ABSOLUTE DIFFERENCE between the white lamp spectra and their mean
# with microscope
plot.detector.whitelamp(data=makeSpectraPlotable(detector.absDifference[[1]][, -c(2:3)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation+45, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Absolute Difference (with detector)",
                        ylab="abs. difference") 
# with microscope, only the extrema
plot.detector.whitelamp(data=makeSpectraPlotable(detector.absDifference[[1]][, c(1, 7, 16)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation+45, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Absolute Difference (with detector)",
                        ylab="abs. difference")
# without microscope
plot.detector.whitelamp(data=makeSpectraPlotable(detector.absDifference[[2]][, -c(2:3)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Absolute Difference (without detector)",
                        ylab="abs. difference")

# Plot the RELATIVE DIFFERENCE between the white lamp spectra and their mean
# with microscope
plot.detector.whitelamp(data=makeSpectraPlotable(detector.relDifference[[1]][, -c(2:3)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation+45, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Relative Difference (with detector)",
                        ylab="rel. difference") +
  coord_cartesian(ylim = c(-0.22, 0.22))
# with microscope, only the extrema
plot.detector.whitelamp(data=makeSpectraPlotable(detector.relDifference[[1]][, c(1, 7, 16)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation+45, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Relative Difference (with detector)",
                        ylab="rel. difference")
# without microscope
plot.detector.whitelamp(data=makeSpectraPlotable(detector.relDifference[[2]][, -c(2:3)], 
                                                 colorFunc=function(polariserRotation) {mod(polariserRotation, 180) %>% `-`(.,90) %>% abs(.)} ), 
                        title="Relative Difference (without detector)",
                        ylab="rel. difference")

```

